The Splashback Radius of Planck-SZ clusters

### 2019-01-09 Paper_v2/RSP_paper_new.tex
Some more corrections by Dominik in regard of referee report

We caution however that the cut we use to define our samples was
defined based on spectroscopic galaxies, which tend to be brighter
than the typical galaxies we use for the cross-correlation. As we use
galaxies at fainter magnitudes for the cross-correlation, the
photometric errors increase dramatically and can scatter many more of
the red galaxies into the blue galaxy sample. We report on
our investigations in Appendix~\ref{sec:Errors} as a cautionary tale,
and to guide future efforts to establish the splashback radius in the
blue galaxy population. We show that given the current state of the
data we can marginally exclude a contamination of the correlation
function of blue galaxies from the red galaxy population but
appropriate caution is warranted in the interpretation or use of the
results derived using the color separated galaxy populations.

@@

%\begin{figure*}
%\centering{
%    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
%\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
%of the matched galaxies versus their redshifts, where the red dots correspond
%to galaxies identified as red from the SDSS spectroscopic colors and blue dots
%correspond to galaxies identified as blue, respectively. The black, solid line
%indicates the spline cut separating the two populations and excluding the red 
%galaxies from the blue population at a confidence level of $3 \sigma$.}
%   \label{fig:g-r_vs_z} 
%\end{figure*}

To infer the color cut which separates star forming (blue) galaxies from the
quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
sample to its Pan-STARRS photometry. 
The SDSS spectroscopic sample is however quite shallow, 
and thus consists of galaxies that are brighter than the Pan-STARRS 
galaxies that we wish to cross-correlate. At fainter magnitudes, we can 
expect red galaxies to scatter into the blue population 
due to photometric errors, potentially contaminating the
correlation function measurement. This could erroneously cause the
splashback feature observed in the blue population. Therefore, we
need to assess the possiblity of such a contamination.

@@

% \begin{figure}
% \centering{
%     \includegraphics[scale=0.6]{best_hist_58.pdf}}
% \caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
% of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
% whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
% survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
% distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
%     \label{fig:histogram}•
% \end{figure}

>>>>

\textbf{This result is in contradiction to the findings of \citet{baxter2017halo}, who find no splashback feature in the blue galaxy population. At the current state it is not clear how those different results emerge. It might be that, in contrast to our SZ selected cluster sample, there is simply no splashback feature present in the galaxy cluster sample used by \citet{baxter2017halo}, which was constructed using the REDMAPPER algorithm on SDSS data. Further, the separation of the galaxies by color used by \citet{baxter2017halo} is fundamentaly different from our approach. They use K-corrected magnitudes from the SDSS dataset, whereas we avoid using K-corrections but instead use a redshift dependent color cut.}

We caution that the cut we use to define our color-separated samples was
defined based on spectroscopic galaxies, which tend to be brighter
than the typical galaxies we use for the cross-correlation. As we use
galaxies at fainter magnitudes for the cross-correlation, the
photometric errors increase dramatically and can scatter many more of
the red galaxies into the blue galaxy sample. We report on
our investigations in Appendix~\ref{sec:Errors} as a cautionary tale,
and to guide future efforts to establish the splashback radius in the
blue galaxy population. We show that given the current state of the
data we can marginally exclude a contamination of the correlation
function of blue galaxies from the red galaxy population but
appropriate caution is warranted in the interpretation or use of the
results derived using the color separated galaxy populations.

@@

To infer the color cut which separates star forming (blue) galaxies from the
quenched (red) galaxy population, we cross-matched the SDSS spectroscopic
sample to its Pan-STARRS photometry. In Figure~\ref{fig:g-r_vs_z}, we show the
plot of the Pan-STARRS $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ color as a 
function of redshift, and the color cut we use in our analysis. 
The SDSS spectroscopic sample is however quite shallow, 
and thus consists of galaxies that are brighter than the Pan-STARRS 
galaxies that we wish to cross-correlate. At fainter magnitudes, we can 
expect red galaxies to scatter into the blue population 
due to photometric errors, potentially contaminating the
correlation function measurement. This could erroneously cause the
splashback feature observed in the blue population. Therefore, we
need to assess the possiblity of such a contamination.

@@

\begin{figure*}
\centering{
    \includegraphics[width= 0.5\textwidth]{color_vs_z.pdf}}
\caption{Scatter plot showing the $(g_{\mathrm{P1}}-r_{\mathrm{P1}})$ colors
of the matched galaxies versus their redshifts, where the red dots correspond
to galaxies identified as red from the SDSS spectroscopic colors and blue dots
correspond to galaxies identified as blue, respectively. The black, solid line
indicates the spline cut separating the two populations and excluding the red 
galaxies from the blue population at a confidence level of $3 \sigma$.}
   \label{fig:g-r_vs_z} 
\end{figure*}
% \begin{figure}
% \centering{
%     \includegraphics[scale=0.6]{best_hist_58.pdf}}
% \caption{Histogram of the $g_{PS} - r_{PS}$ colors of the galaxies in a certain redshift bin for illustration
% of the contamination estimation. The solid, colored curves indicate the initially fitted Gaussian distributions,
% whereas the dashed curves represent the Gaussian distributions broadened by the photometric errors of the Pan-STARRS
% survey. The black, vertical line indicates the cut, separating the two galaxy populations as inferred from the original
% distributions. The cut excludes red galaxies from being characterized as blue galaxies at $3/sigma$ confidence.}
%     \label{fig:histogram}•
% \end{figure}
